\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage[spanish]{babel}
\usepackage[utf8]{inputenc}
\usepackage{multicol}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Juan Carlos Castrejón Estrada}
\address{github.com/JCastrejonE}
\address{México, Ciudad de México · 04230}
\address{castrejon@ciencias.unam.mx \\ (52) · 55 · 41 · 78 · 47 · 43}

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Universidad Nacional Autónoma de México} \hfill {\em 2015 - 2021 (expected)}
\\ Facultad de Ciencias
\\ Bachelor's Degree in Computer Science

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Facebook}{\em June 2020 - September 2020}{Production Engineer Intern}{Menlo Park, California (remote)}
\item Business Integrity Ads team.
\item Worked on an infrastructure integration project with direct impact over Facebook's ads consistency.
\end{rSubsection}

\begin{rSubsection}{Oracle}{\em July 2019 - January 2020}{Software Engineer Intern}{México, Guadalajara}
\item Database team, focused on data layer.
\item Securefile LOBs and DBFS research.
\end{rSubsection}

\begin{rSubsection}{Quince Rooftop}{\em March 2017 - January 2019}{Server administrator / Full Stack developer / Manager}{México, Cd. de México}
\item API management for a restaurant live statistics system using NodeJS and MongoDB.
\item Tool for live frame capture of most RTSP surveillance cameras.
\item Radio station server for live music streaming for a restaurant.
\item Customer feedback system using ReactJS and Flux pattern.
\end{rSubsection}

\begin{rSubsection}{Laboratorio Nacional de Canalopatías, UNAM}{\em June 2015 - February 2016}{Web Developer}{México, Cd. de México}
\item Design and development of the administration system for the website, using PHP and MySQL.
\end{rSubsection}

\end{rSection}


%----------------------------------------------------------------------------------------
%	RELEVANT COURSES SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Additional Training}

\begin{multicols}{2}
Docker and Kubernetes. \hfill{\em(48 hours)} \\
Evolutionary Algorithms. \hfill{\em(48 hours)} \\
Heuristic Optimization. \hfill{\em(48 hours)} \\
Agent Based Simulation. \hfill{\em(48 hours)} \\
Malware Analysis. \hfill{\em(20 hours)} \\
Computer Forensics. \hfill{\em(20 hours)}
\end{multicols}

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming Languages &  Bash, C, C++, Java, JavaScript, PHP, Python, SQL \\
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	PERSONAL SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Personal}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Profile & Passionate about technology and highly interested on learning from other's \\
& experience. Very proactive, always aiming to keep on top of new releases. \\
Languages & Spanish \emph{(native)}, English \emph{(advanced)}, French \emph{(basic)}, Japanese \emph{(basic)} \\
Hobbies & Board Games, ICPC problem solving, Capture the flag contests \\
Date of Birth & August 24th, 1996
\end{tabular}

\end{rSection}

\end{document}
